\begin{thebibliography}{99}
\bibitem{arratia} Richard A. Arratia. Coalescing Brownian motions on
  the line. PhD thesis, University of Wisconsin, Madison, 1979.
\bibitem{billingsley} Patrick Billingsley. Convergence of probability
  measures. Wiley Series in Probability and Statistics: Probability
  and Statistics. John Wiley \& Sons Inc., New York, 1999.
\bibitem{fontes-et-al} L. R. G. Fontes, M. Isopi, C. M. Newman, and
  K. Ravishankar. The Brownian web: characterization and
  convergence. Ann. Probab., 32(4):2857--2883, 2004.
\bibitem{norris-turner-convergence-to-bw} James Norris and Amanda
  Turner. Planar aggregation and the coalescing Brownian flow.
  arXiv:math.PR/0810.0211, 2008.
\bibitem{norris-turner-planar-aggregation} James Norris and Amanda
  G. Turner. Planar aggregation and the coalescing Brownian
  flow. arXiv:math.PR/0810.0211, 2008.
\bibitem{schramm-smirnov}
  Oded Schramm, Stanislav Smirnov, and Christophe Garban
  On the scaling limits of planar percolation
  Ann. Probab. Volume 39, Number 5 (2011), 1768-1814.
\bibitem{toth-werner} Balint Toth and Wendelin Werner. The true
  self-repelling motion. Probab. Theory Related Fields,
\bibitem{tsirelson-vershik}
  Tsirelson, B.S., Vershik, A.M. (1998): Examples of nonlinear continuous
  tensor products of measure spaces and non-Fock factorizations. Reviews
  in Mathematical Physics 10:1, 81--145.
\bibitem{tsirelson-lecture-course}
  Tsirelson, Boris
  White noises, black noises and other scaling limits
  Lecture course, Tel Aviv University, 2002
\bibitem{tsirelson-scaling-limit-noise-stability}
  Boris Tsirelson
  Scaling Limit, Noise, Stability
  Lect. Notes Math. 1840 (2004), 1-106.
  111(3):375--452, 1998.
\bibitem{tsirelson-nonclassical-stochastic-flows} Boris Tsirelson,
  Nonclassical stochastic flows and continuous products
  http://arxiv.org/abs/math/0402431v3
  Probability Surveys 1 (2004) 173-298
\bibitem{tsirelson-completion} Boris Tsirelson, Noise as a Boolean
  algebra of sigma-fields. I. Completion, http://arxiv.org/abs/1107.3042v2
\bibitem{tsirelson-classicality-blackness-spectrum} Boris Tsirelson,
  Noise as a Boolean algebra of sigma-fields. II. Classicality,
  blackness, spectrum
  http://arxiv.org/abs/1109.1690
\end{thebibliography}
