{
\newcommand{\factor}[2]{\mathcal{F}_{#1 #2}}
\newcommand{\commafactor}[2]{\mathcal{F}_{#1,#2}}
\newcommand{\simplex}{\mathcal{S}}

\section{Definition of the Brownian web on horizontal strips}

\begin{definition}
  A pair of independent-coalescing Brownian motions is a pair of
  stochastic processes $(X, X')$ such that $X_t$ is defined for $t \in
  [s, \infty)$, say, and $X'_t$ for $t \in [s', \infty)$, say.  $X$
      and $X'$ are Brownian motions independent until time $T = \inf
      \{ t \ge s \max s' : X_t = X'_t\}$, and for $t \ge T$ $X_t =
      X'_t$.
\end{definition}

\begin{definition}
  Let $\simplex$ = $\{(s, t) \in \R^2 : s \le t\}$
\end{definition}

\newcommand{\webnoargs}{\phi}
\newcommand{\web}[3]{\webnoargs_{{#1}{#2}}(#3)}

\begin{definition}
  A Brownian web on a probability space $\Omega$ is a
  jointly-measurable mapping $\webnoargs : \Omega \cross \simplex \cross
  \R \to \R$, $(\omega, s, t, x) \mapsto \web{s}{t}{x}$ (we supress
  $\omega$ in the notation) such that for fixed pairs of starting
  points $(s, x)$ and $(s', x')$, the pair of processes $(\web{s}
  {\cdot}{x}, \web{s'}{\cdot}{x'})$ is a pair of independent-coalescing
  Brownian motions.
\end{definition}

\begin{definition}
  \newcommand{\T}{\stripleavetime{f}}
  \label{def:restrict}
  From a path $f : [s, \infty) \to \R$ we define ``$f$ stopped on
    leaving the interval $I$'' to be the map $\restrict{I}{f} : [s,
      \infty) \to \R$ given by $\restrict{I}{f}(t) = f(t \minsym \T)$
      where $\T = \inf\{ t : f(t) \not\in I \}$.
\end{definition}

\newcommand{\brownianwebnoise}{collection of horiztontal
  sub-$\sigma$-algebras of the Brownian web}

\begin{definition}
  The \brownianwebnoise{} is an
  association of a $\sigma$-algebra $\factor{y}{z}$ to each $(y, z)
  \in \simplex$, generated by the following collection of paths:
  $\{ \restrict{(y,z)}{t \mapsto \web{s}{t}{x}} : s, x \in \R \}$
\end{definition}

\begin{note}
  \newcommand{\F}{\mathcal{F}}

  For $\sigma$-algebras $\F_a$, $\F_b$, $\F_c$ we write $\F_a = \F_b
  \tensor \F_c$ when $\F_b$ and $\F_c$ are independent, and $\F_a =
  \F_b \vee \F_c$ (up to sets of measure $0$).
\end{note}

\begin{theorem}
  The \brownianwebnoise{}
  is a continuous product of probability spaces in the sense that
  for each $x \le y \le z$, $\factor{x}{y} \tensor \factor{y}{z} =
  \factor{x}{z}$.
  See 3c1 Definition of
  \cite{tsirelson-nonclassical-stochastic-flows}.
\end{theorem}

\begin{theorem}
  The \brownianwebnoise{} is a noise in the sense that it is a
  continuous product of probability spaces with a translation.
  See 3d1 Definition of
  \cite{tsirelson-nonclassical-stochastic-flows}.
\end{theorem}

\FIXME{}{Need to make a comment that the obvious translation works.}

\begin{theorem}
  The collection of two-dimensional sub-$\sigma$-algebras of the
  Brownian web is a two-dimensional noise, and moreover it is black.
\end{theorem}

\begin{proof}
  We know that the one-dimensional noise consisting of the vertical
  collection of sub-$\sigma$-algebras is black.  By general arguments
  on spectral sets this implies that the two-dimensional noise is
  black.  See \cite{tsirelson-classicality-blackness-spectrum}.
\end{proof}

\section{Definition of the ``resampled'' process}

\newcommand{\reservoir}{\mathcal{G}}

\newcommand{\twostrips}{\commafactor{-\infty}{0} \tensor \commafactor{0}{\infty}}
\newcommand{\onestrip}{\commafactor{-\infty}{\infty}}
\newcommand{\twostripsreservoir}{\twostrips \tensor \reservoir}

\begin{definition}
Given a Brownian web $\webnoargs$, fix a starting point $(s,x)$ and write
$\sampled$ for the random process $t \mapsto \web{s}{t}{x}$
(which is a Brownian motion).
\end{definition}

{
\newcommand{\joinernoargs}{\psi}
\newcommand{\joiner}[2]{\joinernoargs_{{#1}{#2}}}
\begin{definition}
  We define $\resamplede$, a ``perturbed'' version of $\sampled$, as
  follows.

  Let $\joiner{s}{t}$ be the increments (between times $s \le t$) of
  some Brownian motion independent of $\webnoargs$ (measurable with
  respect to $\reservoir$, say, where $\reservoir$ is independent of
  $\commafactor{\infty}{-\infty}$).

  \begin{itemize}
  \item Starting from time $s$, follow the path $\web{s}{\cdot}{x}$
    until it hits $0$, at time $S_1$, say.
  \item Then follow $\joiner{S_1}{\cdot}$ until it hits $\pm \epsilon$, at
    time $T_1$, say.
  \item Then follow $\web{T_1}{\cdot}{\pm \epsilon}$ until it hits $0$, at
    time $S_2$, say.
  \item Continue indefinitely in this inductive fashion.
  \end{itemize}
\end{definition}
}

\begin{obs}
  \label{obs:2d-proc}
  A rough description of the coupled pair $(\sampled, \resamplede)$
  follows.

  \FIXME{}{}
\end{obs}

\begin{obs}
  $\resamplede$ is $\twostripsreservoir$-measurable.
\end{obs}

\begin{lemma}
  $\resamplede \to \sampled$ uniformly on compacts in probability as $\epsilon \to 0$.
\end{lemma}

\begin{cor}
  \label{cor:sampled-twostripsreservoir-meas}
  $\sampled$ is $\twostripsreservoir$-measurable.
\end{cor}

\begin{theorem}
  $\twostrips = \onestrip$
\end{theorem}

\begin{proof}
  $\onestrip$ is generated by random variables of the form $X$, thus
  by Corollary \ref{cor:sampled-twostripsreservoir-meas} $\onestrip
  \subseteq \twostripsreservoir$.  Since $\onestrip$ is
  independent of $\reservoir$ a simple result on tensor products of
  Hilbert spaces (for example (1c1), p5 of
  \cite{tsirelson-completion}) shows
  that $\onestrip \subseteq \twostrips$.
\end{proof}
}
